---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Using Python from RStudio

The goal of this meetup is to help you to use Python from RStudio.

## Who is the audience?

Anyone who wants to use Python from RStudio.

## Why is this important?

Many Data Science teams today are bilingual, leveraging both R and Python in
their work. Typically, each language is used from a different IDE but switching
IDE is painful, and many of us at 2DII are already familiar with RStudio. We
would like RStudio to be the single home for both R and Python.

Objectives:

* Use a specific, and complex Python environment from RStudio.
* Run complex Python code in an rmarkdown document from Rstudio.
* Run complex Python code in an interactive console from RStudio.

## Demo

## Setup

* [Anaconda](https://docs.continuum.io/anaconda/) is a collection of software
for data science with Python and R. It contains a package and environment
manager, which helps users manage a collection of over 7,500+ open-source
packages.

* [reticulate](https://rstudio.github.io/reticulate/) is an R package that
enables the interface between R and Python. If available it's automatically used
by rmakrkdown and RStudio.

* `RETICULATE_PYTHON` is an optional environment variable to control which copy of Python reticulate chooses to bind to. It should be set to the path to a Python interpreter, and that interpreter can either be:
    * A standalone system interpreter,
    * Part of a virtual environment,
    * Part of a Conda environment.

```{r}
Sys.setenv(RETICULATE_PYTHON = "/home/mauro/anaconda3/bin/python")
reticulate::py_config()
```

### Example code

```{python}
import nltk
import spacy
# conda install -c conda-forge spacy-model-en_core_web_sm

sent = "Please book my flight to California."

tokenized_sent_nltk = nltk.sent_tokenize(sent)
[nltk.pos_tag(nltk.word_tokenize(word)) for word in tokenized_sent_nltk]

nlp = spacy.load("en_core_web_sm")
spacy_doc = nlp(sent)

print(spacy_doc)

for token in spacy_doc:
    print(token.text, token.pos_)
```

## Resources

* YouTube [playlist](https://bit.ly/ds-incubator-videos).
* The
[ds-incubator](https://github.com/2DegreesInvesting/ds-incubator#ds-incubator)
project.
* [Ideas](https://bit.ly/dsi-ideas) for future meetups.
* [RStudio: A single home for R & Python (webinar)](https://rstudio.com/resources/webinars/rstudio-a-single-home-for-r-and-python/).
