---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Using Python from RStudio

The goal of this meetup is to help you to use Python from RStudio.

## Who is the audience?

Anyone who wants to use Python from RStudio.

## Why is this important?

Many Data Science teams today are bilingual, leveraging both R and Python in
their work. Typically, each language is used from a different IDE but switching
IDE is painful, and many of us at 2DII are already familiar with RStudio. We
would like RStudio to be the single home for both R and Python.

Objectives:

* Create a Python environment.
* Install Python packages from RStudio.
* Use a Python environment.
* Run an rmarkdown document from Rstudio -- with both R and Python.
* Run a Python script from RStudio.
* Run Python code interactively from RStudio.

## Demo

## Setup

Use the R interface to Python

```{r}
# install.packages("reticulate")
library(reticulate)
```

It's recommended to use a dedicated virtual environment.

* Install Python itself.

```{r}
version <- "3.9.12"
install_python(version)
virtualenv_create("r-reticulate", version = version)
```

* Install Python packages.

```{r}
use_virtualenv("r-reticulate")

virtualenv_install("r-reticulate", "nltk")
virtualenv_install("r-reticulate", "spacy")
virtualenv_install("r-reticulate", "en_core_web_sm")
```

### Example code

```{python}
import nltk
import spacy
import en_core_web_sm

nltk.download('punkt')
nltk.download('averaged_perceptron_tagger')

sent = "Please book my flight to California."

tokenized_sent_nltk = nltk.sent_tokenize(sent)
[nltk.pos_tag(nltk.word_tokenize(word)) for word in tokenized_sent_nltk]

# nlp = spacy.load("en_core_web_sm")
nlp = en_core_web_sm.load()
spacy_doc = nlp(sent)
for token in spacy_doc:
    print(token.text, token.pos_)
```

## Resources

* YouTube [playlist](https://bit.ly/ds-incubator-videos).
* The
[ds-incubator](https://github.com/2DegreesInvesting/ds-incubator#ds-incubator)
project.
* [Ideas](https://bit.ly/dsi-ideas) for future meetups.
* [RStudio: A single home for R & Python (webinar)](https://rstudio.com/resources/webinars/rstudio-a-single-home-for-r-and-python/).
